MCTS Applied to Co-operative Problems

### 2015-08-01 Report/response.tex

\documentclass{article}
\title{Response}

\begin{document}
\maketitle
\section{Letters to the reviewers}
\subsection{Review 1 (Reviewer )}
\subsection{Review 2 (Reviewer )}
\subsection{Review 3 (Reviewer )}
\subsection{Review 4 (Reviewer )}
\subsection{Review 5 (Reviewer )}
\end{document}

### 2015-08-01 Report/response.tex

\documentclass{article}
\title{Response}

\begin{document}
\maketitle
\section{Letters to the reviewers}
\subsection{Review 1 (Reviewer )}
We have corrected the typo in the definition of Walls in the problem domain section.
\subsection{Review 2 (Reviewer )}
\subsection{Review 3 (Reviewer )}
We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.

We have corrected the typo in the definition of Walls in the problem domain section.
\subsection{Review 4 (Reviewer )}
\subsection{Review 5 (Reviewer )}
\end{document}

### 2015-08-01 Report/response.tex

\documentclass{article}
\title{Response}

\begin{document}
\maketitle
\section{Letters to the reviewers}
\subsection{Review 1 (Reviewer )}
We have corrected the typo in the definition of \emph{Walls} in the problem domain section.

We have changed the description of \emph{Doors} to better reflect what they look like when open.
\subsection{Review 2 (Reviewer )}
\subsection{Review 3 (Reviewer )}
We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.

We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
\subsection{Review 4 (Reviewer )}
\subsection{Review 5 (Reviewer )}
\end{document}

### 2015-08-01 Report/ceec.tex
Fixed the UCT Definition error
Fixed the typo for the walls
Fixed the description of doors to show what they look like when open
Added definition for the floor

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}
\newacronym{mas}{MAS}{Multi-Agent Systems}
\newacronym{maga}{MAGA}{Macro Action Genetic Algorithm}
\newacronym{ai}{AI}{Artificial Intelligence}

@@

\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Doors} are rendered in Black.}
\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect. \emph{Goals} are rendered in Yellow}
\end{itemize}

>>>>

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Upper Confidence bound applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}
\newacronym{ga}{GA}{Genetic Algorithm}
\newacronym{mas}{MAS}{Multi-Agent Systems}
\newacronym{maga}{MAGA}{Macro Action Genetic Algorithm}
\newacronym{ai}{AI}{Artificial Intelligence}

@@

\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Floor - } Floors are passable, and are rendered in Grey.}
\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.}
\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue whilst closed, and are invisible when open}
\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect. \emph{Goals} are rendered in Yellow}
\end{itemize}
